Performance portability of an intermediate-complexity atmospheric research model in coarray Fortran

### 2017-10-05 main.tex
Committing edits from August 16.
Delete authordraft documentclass
This step prepares the paper for final submission by
1. Removing watermarks
2. Removig line numbers
Add short title for use in page headers.

\documentclass[sigconf, authordraft]{acmart}

@@

\begin{document}
\title{Performance portability of an intermediate-complexity atmospheric research model in coarray Fortran}
%\titlenote{Produces the permission block, and
%  copyright information}
\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
We examine the scalability and performance of an open-source, \gls{caf} \gls{mini-app} that solves
several parallel, numerical algorithms known to dominate the execution of \gls{icar}~\cite{gutmann2016intermediate} model,
a package developed at the \gls{ncar}.
The \gls{mini-app} uses standard Fortran 2008, including several Fortran 2008 implementations of the collective
subroutines defined in the Committee Draft of the upcoming Fortran 2015 standard.  The ability of \gls{caf} to run atop various
communication layers and the increasing \gls{caf} compiler availability facilitated evaluating several compilers,
runtime libraries and hardware platforms.  Results are presented for the GNU and Cray compilers, each of which offers
different parallel runtime libraries employing one or more communication layers, including \gls{mpi}, OpenSHMEM, and proprietary
alternatives.  We studied performance on multi- and many-core processors in distributed memory.  The
results show promising scaling behavior across a range of hardware, compiler, and runtime choices
on platforms ranging up to 100,000 cores.
\end{abstract}

>>>>

\documentclass[sigconf]{acmart}
%\documentclass[sigconf, authordraft]{acmart}

@@

\begin{document}
\title[Performance portability of coarray-ICAR]{Performance portability of an intermediate-complexity atmospheric research model in coarray Fortran}
%\titlenote{Produces the permission block, and
  %copyright information}
\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
We examine the scalability and performance of an open-source, \gls{caf} \gls{mini-app} that solves
several parallel, numerical algorithms known to dominate the execution of \gls{icar}~\cite{gutmann2016intermediate} model,
a package developed at the \gls{ncar}.
The \gls{mini-app} uses standard Fortran 2008, including several Fortran 2008 implementations of the collective
subroutines defined in the Committee Draft of the upcoming Fortran 2015 standard.  The ability of \gls{caf} to run atop various
communication layers and the increasing \gls{caf} compiler availability facilitated evaluating several compilers,
runtime libraries and hardware platforms.  Results are presented for the GNU and Cray compilers, each of which offers
different parallel runtime libraries employing one or more communication layers, including \gls{mpi}, OpenSHMEM, and proprietary
alternatives.  We studied performance on multi- and many-core processors in distributed memory.  The
results show promising scaling behavior across a range of hardware, compiler, and runtime choices
on platforms ranging up to $\sim$100,000 cores.
\end{abstract}
